\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-09 analysis/RD design analysis.Rmd
modified:   analysis/RD design analysis.Rmd 	deleted:    analysis/RD-design-analysis.tex 	deleted:    analysis/donut_robust.tex 	modified:   figures/RD_Plot_1st_Order.pdf 	new file:   figures/RD_Plot_1st_Order_robust.pdf 	modified:   figures/RD_Plot_2nd_Order.pdf 	new file:   figures/RD_Plot_2nd_Order_robust.pdf 	modified:   figures/RD_Plot_3rd_Order.pdf 	new file:   figures/RD_Plot_3rd_Order_robust.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscr

```{r}
# these are the packages that we need to import
library(haven)
library(rdd)
library(ggplot2)
library(dplyr)
library(rdrobust)
library(plm)
library(xtable)
library(pander) # this is for table showing
library(latex2exp) # this is to export it
setwd("E:/umich/RealEstateBrokerage-main")
# need to place data on the base directory
data <- read_dta("template.dta")
working_directory <-"E:/umich/RealEstateBrokerage"
```

@@

```{r}
h = 0.066
cutoff = 0.41
running_var = panel_data$nearest_store_distances

filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]

# Export the first RD plot to its own PDF file
pdf("RD_Plot_1st_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 1,
       title = "RD-plot 1st order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community")
dev.off() # Close the PDF device

# Export the second RD plot to its own PDF file
pdf("RD_Plot_2nd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 2,
       title = "RD-plot 2nd order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community")
dev.off() # Close the PDF device

# Export the third RD plot to its own PDF file
pdf("RD_Plot_3rd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot 3rd order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community")
dev.off() # Close the PDF device
```

@@

@@

1. Donut Hole: Exclude observations close to the cutoff and estimate the effect with the remaining data. If the discontinuity persists despite the absence of data around the cutoff, this provides evidence against a model misspecification.
2. Mccrary (2008) test: Conduct a McCrary density test to check if there is a discontinuity in the density of the running variable at the cutoff. A significant discontinuity may suggest manipulation or sorting around the cutoff.
3. Placebo test: If you have pre-treatment covariates, you can test whether these covariates also jump at the cutoff. If they do, this might suggest manipulation or a violation of the RD design assumptions. If they don’t, it strengthens the case for a true treatment effect.

@@

```{r}
cutoff
donut_width <- 0.011
panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                 panel_data$nearest_store_distances <= (cutoff + donut_width)),]
result_donut <- rdrobust(y = panel_data_donut$ln_income, 
                         x = panel_data_donut$nearest_store_distances, 
                         c = cutoff,
                        p = 1, h = 0.066, b = 0.135)
pander(cbind(result_donut$coef, result_donut$pv))
print(result_donut)
```

```{r}
perform_rd_analysis <- function(cutoff, donut_width, h, b) {
  # select the data that we need
  panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                   panel_data$nearest_store_distances <= (cutoff + donut_width)),]
  # run the rdrobust result
  result_donut <- rdrobust(y = panel_data_donut$ln_income, 
                           x = panel_data_donut$nearest_store_distances, 
                           c = cutoff,
                           p = 1, h = h, b = b)
  # return the coefficient and the p value
  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1])
  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1])
  robust <- c("Robust", 
              format(result_donut$coef[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$se[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE))

  # combine the results
  result_table <- rbind(conventional, bias_corrected, robust)
  colnames(result_table) <- c("Method", "Coef", "SE", "p-value")
  return(result_table)
}

cutoff = 0.41
donut_widths <- c(0.01, 0.0125, 0.015, 0.0175, 0.02, 0.0225, 0.025)
results <- list()

for (donut in donut_widths) {
  result <- perform_rd_analysis(cutoff, donut, 0.066, 0.135)
  results[[paste0("donut_", donut)]] <- result
}

@@

```{r}
perform_rd_analysis <- function(cutoff, donut_width, h, b) {
  # select the data that we need
  panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                   panel_data$nearest_store_distances <= (cutoff + donut_width)),]
  # run the rdrobust result
  result_donut <- rdrobust(y = panel_data_donut$ln_income, 
                           x = panel_data_donut$nearest_store_distances, 
                           c = cutoff, covs = panel_data_donut[, control_variables],
                           p = 1, h = h, b = b)
  # return the coefficient and the p value
  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1])
  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1])
  robust <- c("Robust", 
              format(result_donut$coef[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$se[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE))

  # combine the results
  result_table <- rbind(conventional, bias_corrected, robust)
  colnames(result_table) <- c("Method", "Coef", "SE", "p-value")
  return(result_table)
}

cutoff = 0.41
donut_widths <- c(0.01, 0.0125, 0.015, 0.0175, 0.02, 0.0225, 0.025)
results_with_control <- list()

for (donut in donut_widths) {
  result <- perform_rd_analysis(cutoff, donut, 0.066, 0.135)
  results_with_control[[paste0("donut_", donut)]] <- result
}
```

```{r}
# with controls
combined_results_with_control <- do.call(rbind, lapply(names(results_with_control), function(donut) {
  result <- results_with_control[[donut]]
  robust_result <- result[result[, "Method"] == "Robust", ]
  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4])
}))
colnames(combined_results_with_control) <- c("Donut Width", "Method", "Coef", "SE", "p-value")

# without controls
combined_results <- do.call(rbind, lapply(names(results), function(donut) {
  result <- results[[donut]]
  robust_result <- result[result[, "Method"] == "Robust", ]
  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4])
}))
colnames(combined_results) <- c("Donut Width", "Method", "Coef", "SE", "p-value")

merged_results <- merge(combined_results_with_control, combined_results, by = c("Donut Width", "Method"))
merged_results_df <- as.data.frame(merged_results)

colnames(merged_results_df) <- c("Donut Width", "Method", "Coef", "SE", "p-value", "Coef", "SE", "p-value")

@@

latex_code <- gsub("\\\\begin\\{tabular\\}\\{llllllll\\}\n  \\\\hline\n", 
                   "\\\\begin{tabular}{llllllll}\n  \\\\hline\n &  & \\\\multicolumn{3}{c}{Without Control} & \\\\multicolumn{3}{c}{With Control} \\\\\\\\\n", 
                   latex_code)

@@

```{r}
# Give it the running variable and the cutpoint
# it will automatically produce a plot and select the number of bins and the bandwidth
# The output will be the p-value for the presence of a discontinuity
DCdensity(filtered_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
```

@@

```{r}
testing_variables <- c("pop", "light", "price_concession", "ln_end_price", "ln_nego_changes", "ln_watch_time", "green_ratio", "bedroom", "ln_watch_people", "living_room", "ln_negotiation_period", "museum", "kind", "mid", "sub", "house_age", "total_building")

@@

for (validation in testing_variables) {
  rd_result <- rdrobust(y = panel_data[[validation]], x = panel_data$nearest_store_distances,
                        c = 0.41, h = 0.066, b = 0.135,
                        bwselect = "mserd", kernel = "triangular")

@@

```{r}
cutoffs_width <- c(0.15, 0.2, 0.25, 0.30, 0.35, 0.50, 0.65, 0.7)

results_list <- list()
counter <- 1
for (cutoff in cutoffs_width) {
  # rd_result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, c = cutoff, h = 0.066, b = 0.135, bwselect = "mserd", kernel = "triangular")
  rd_result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances,
                        c = cutoff)

>>>>

```{r}
# these are the packages that we need to import
library(dplyr)
library(haven)
library(rdd)
library(ggplot2)
library(rdrobust)
library(plm)
library(xtable)
library(pander) # this is for table showing
library(latex2exp) # this is to export it
setwd("E:/umich/RealEstateBrokerage-main")
# need to place data on the base directory
data <- read_dta("template.dta")
working_directory <-"E:/umich/RealEstateBrokerage"
set.seed(130)
```

@@

```{r}
ci_level = 95
h = 0.063
cutoff = 0.41
running_var = panel_data$nearest_store_distances
running_var <- as.numeric(running_var)
filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]

# Export the first RD plot to its own PDF file
pdf("RD_Plot_1st_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 1,
       title = "RD-plot 1st order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community", col.dots = "blue", kernel = "triangular")
dev.off() # Close the PDF device

# Export the second RD plot to its own PDF file
pdf("RD_Plot_2nd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 2,
       title = "RD-plot 1st order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community", col.dots = "blue", kernel = "triangular")
dev.off() # Close the PDF device

# Export the third RD plot to its own PDF file
pdf("RD_Plot_3rd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot 3rd order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community", col.dots = "blue", kernel = "triangular")
dev.off() # Close the PDF device
```

```{r}
ci_level = 95
h = 0.063
cutoff = 0.41
running_var = panel_data$nearest_store_distances
running_var <- as.numeric(running_var)
filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]

# Export the first RD plot to its own PDF file
pdf("RD_Plot_1st_Order_robust.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 1,
       title = "RD-plot 1st order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community", col.dots = "blue", kernel = "triangular")
dev.off() # Close the PDF device

# Export the second RD plot to its own PDF file
pdf("RD_Plot_2nd_Order_robust.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 2,
       title = "RD-plot 1st order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community", col.dots = "blue", kernel = "triangular")
dev.off() # Close the PDF device

# Export the third RD plot to its own PDF file
pdf("RD_Plot_3rd_Order_robust.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot 3rd order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community", col.dots = "blue", kernel = "triangular")
dev.off() # Close the PDF device
```

```{r}
bw_methods <- c("mserd", "cerrd")
kernel_list <- c("uniform", "triangular")
results_list <- list()
counter <- 1
for (bw_method in bw_methods) {
    for (kernel_in in kernel_list){
        result <- rdrobust(y = panel_data$income, x = panel_data$nearest_store_distances, 
                     c = 0.41,
                     p = 1, 
                     bwselect = bw_method, kernel = kernel_in)

```{r}
result <- rdrobust(y = panel_data$income, x = panel_data$nearest_store_distances, 
                     c = 0.41,
                     p = 1, 
                     bwselect = "mserd", kernel = "triangular")
```

```{r}
print(result)
```

@@

        results_list[[counter]] <- data.frame(
        Method = bw_method,
        Kernel = kernel_in,
        Estimate = format(result$coef[1], digits = 3, scientific = FALSE),
        SE = format(result$se[1], digits = 3, scientific = FALSE),
        Z = format(result$z[1], digits = 3, scientific = FALSE),
        PValue = format(result$pv[1], digits = 3, scientific = FALSE),
        Bandwidth = format(result$bws[1], digits = 3, scientific = FALSE),
        EffectiveObs = effective_obs
    )
        counter <- counter + 1
    }
}
results <- do.call(rbind, results_list)
latex_code <- print(xtable(results, 
                           caption = "RD Estimates with Different Bandwidth Selection Methods and Kernels (robust method with log(income))", 
                           label = "tab:rd_bandwidth_kernel_results_robust"), 
                    include.rownames = FALSE, 
                    type = "latex",
                    print.results = FALSE)
write(latex_code, file = paste(working_directory , "result_tables/rdd_result_summary_robust.tex", sep='/'))
print(results)
```

@@

1. Donut Hole: Exclude observations close to the cutoff and estimate the effect with the remaining data. If the discontinuity persists despite the absence of data around the cutoff, this provides evidence against a model misspecification.
2. Mccrary (2008) test: Conduct a McCrary density test to check if there is a discontinuity in the density of the running variable at the cutoff. A significant discontinuity may suggest manipulation or sorting around the cutoff.
3. Placebo test: If you have pre-treatment covariates, you can test whether these covariates also jump at the cutoff. If they do, this might suggest manipulation or a violation of the RD design assumptions. If they don’t, it strengthens the case for a true treatment effect.
4. The result should robust to little changes across the bandwidth.

@@

```{r}
panel_data <- as.data.frame(panel_data)
panel_data$nearest_store_distances <- as.numeric(panel_data$nearest_store_distances)
```

```{r}
original_model_num <- 30532

perform_rd_analysis <- function(cutoff, donut_width, h, b) {
  # select the data that we need
  panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                   panel_data$nearest_store_distances <= (cutoff + donut_width)),]
  # run the rdrobust result
  result_donut <- rdrobust(y = panel_data_donut$income, 
                           x = panel_data_donut$nearest_store_distances, 
                           c = cutoff,
                           p = 1, h = h, b = b, kernel = "triangular")
  effective_obs <- sum(result_donut$N_h)
  drop_ratio <- (original_model_num - effective_obs) / original_model_num 
  drop_ratio_percentage <- round(drop_ratio * 100, 2)
  # return the coefficient and the p value
  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1], drop_ratio_percentage)
  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1], drop_ratio_percentage)
  robust <- c("Robust", 
              format(result_donut$coef[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$se[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE), drop_ratio_percentage)
  # combine the results
  result_table <- rbind(conventional, bias_corrected, robust)
  colnames(result_table) <- c("Method", "Coef", "SE", "p-value", "Drop Ratio (%)")
  return(result_table)
}

cutoff = 0.41
donut_widths <- c(0.005, 0.0075, 0.01, 0.0125, 0.015, 0.0175, 0.02)
results <- list()

for (donut in donut_widths) {
  result <- perform_rd_analysis(cutoff, donut, 0.063, 0.125)
  results[[paste0("donut_", donut)]] <- result
}

@@

```{r}
results
```

```{r}
original_model_num <- 30532
perform_rd_analysis <- function(cutoff, donut_width, h, b) {
  # select the data that we need
  panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                   panel_data$nearest_store_distances <= (cutoff + donut_width)),]
  # run the rdrobust result
  result_donut <- rdrobust(y = panel_data_donut$income, 
                           x = panel_data_donut$nearest_store_distances, 
                           c = cutoff, covs = panel_data_donut[, control_variables],
                           p = 1, h = h, b = b, kernel = "triangular")
  effective_obs <- sum(result_donut$N_h)
  drop_ratio <- (original_model_num - effective_obs) / original_model_num 
  drop_ratio_percentage <- round(drop_ratio * 100, 2)
  # return the coefficient and the p value
  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1], drop_ratio_percentage)
  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1], drop_ratio_percentage)
  robust <- c("Robust", 
              format(result_donut$coef[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$se[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE), drop_ratio_percentage)

  # combine the results
  result_table <- rbind(conventional, bias_corrected, robust)
  colnames(result_table) <- c("Method", "Coef", "SE", "p-value", "Drop Ratio (%)")
  return(result_table)
}

cutoff = 0.41
donut_widths <- c(0.005, 0.0075, 0.01, 0.0125, 0.015, 0.0175, 0.02)
results_with_control <- list()

for (donut in donut_widths) {
  result <- perform_rd_analysis(cutoff, donut, 0.063, 0.125)
  results_with_control[[paste0("donut_", donut)]] <- result
}
```

```{r}
results_with_control
```

```{r}
# with controls
combined_results_with_control <- do.call(rbind, lapply(names(results_with_control), function(donut) {
  result <- results_with_control[[donut]]
  robust_result <- result[result[, "Method"] == "Robust", ]
  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4], drop_ratio = robust_result[5])
}))
colnames(combined_results_with_control) <- c("Donut Width", "Method", "Coef", "SE", "p-value", "Drop Ratio(%)")

# without controls
combined_results <- do.call(rbind, lapply(names(results), function(donut) {
  result <- results[[donut]]
  robust_result <- result[result[, "Method"] == "Robust", ]
  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4], drop_ratio = robust_result[5])
}))
colnames(combined_results) <- c("Donut Width", "Method", "Coef", "SE", "p-value", "Drop Ratio(%)")

merged_results <- merge(combined_results_with_control, combined_results, by = c("Donut Width", "Method"))
merged_results_df <- as.data.frame(merged_results)
merged_results_df <- merged_results_df %>%
  select(-`Drop Ratio(%).x`)
colnames(merged_results_df) <- c("Donut Width", "Method", "Coef", "SE", "p-value", "Coef", "SE", "p-value", "Drop Ratio(%)")

@@

latex_code <- gsub("\\\\begin\\{tabular\\}\\{lllllllll\\}\n  \\\\hline\n", 
                   "\\\\begin{tabular}{lllllllll}\n  \\\\hline\n &  & \\\\multicolumn{3}{c}{Without Control} & \\\\multicolumn{3}{c}{With Control} & \\\\\\\\\n", 
                   latex_code)

@@

```{r}
# Give it the running variable and the cutpoint
# it will automatically produce a plot and select the number of bins and the bandwidth
# The output will be the p-value for the presence of a discontinuity

robust_bandwidths <- c(0.0773, 0.066, 0.0418, 0.0357)
bandwidths <- c(0.0504, 0.063, 0.0273, 0.0341)
cutoff <- 0.41

perform_mccrary_test <- function(data, cutoff, bandwidths) {
  results <- data.frame(
    Bandwidth = numeric(0),
    Log_Diff = numeric(0),
    SE = numeric(0),
    Z_Stat = numeric(0),
    P_Value = numeric(0)
  )

  for (h in bandwidths) {
    filtered_data <- data[abs(data$nearest_store_distances - cutoff) <= h, ]
    output <- capture.output(test_result <- DCdensity(filtered_data$nearest_store_distances, cutpoint = cutoff, bw = h, verbose = TRUE, plot = FALSE))

    # Extract the required values from the printed output
    log_diff <- as.numeric(sub(".*Log difference in heights is\\s+([-0-9.]+).*", "\\1", output[2]))
    se <- as.numeric(sub(".*with SE\\s+([-0-9.]+).*", "\\1", output[grep("with SE", output)]))
    z_stat <- as.numeric(sub(".*gives a z-stat of\\s+([-0-9.]+).*", "\\1", output[grep("gives a z-stat of", output)]))
    p_value <- as.numeric(sub(".*and a p value of\\s+([-0-9.]+).*", "\\1", output[grep("and a p value of", output)]))

    results <- rbind(results, data.frame(
      Bandwidth = h,
      Log_Diff = log_diff,
      SE = se,
      Z_Stat = z_stat,
      P_Value = p_value
    ))
  }

  return(results)
}

results_bandwidths <- perform_mccrary_test(panel_data, cutoff, bandwidths)
results_robust_bandwidths <- perform_mccrary_test(panel_data, cutoff, robust_bandwidths)

combined_results <- rbind(
  data.frame(
    results_bandwidths
  ),
  data.frame(
    results_robust_bandwidths
  )
)

latex_table <- xtable(combined_results, caption = "McCrary Test Results", label = "tab:mccrary_results")
write(latex_code, file = paste(working_directory , "result_tables/mccrary_results.tex", sep='/'))
```

```{r}
pander(combined_results)
```

@@

```{r}
testing_variables <- c("pop", "light", "price_concession", "ln_end_price", "ln_nego_changes", "ln_watch_time", "green_ratio", "bedroom", "ln_watch_people", "living_room", "ln_negotiation_period", "museum", "kind", "mid", "total_building", "total_resident", "green_ratio", "old", "house_age", "total_building")

@@

for (validation in testing_variables) {
  rd_result <- rdrobust(y = panel_data[[validation]], x = panel_data$nearest_store_distances,
                        c = 0.41, h = 0.063, b = 0.125,
                        kernel = "triangular")

@@

```{r}
cutoffs_width <- c(0.325, 0.35, 0.40, 0.42, 0.45, 0.50, 0.65, 0.7)

results_list <- list()
counter <- 1
for (cutoff in cutoffs_width) {
  # rd_result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, c = cutoff, h = 0.066, b = 0.135, bwselect = "mserd", kernel = "triangular")
  rd_result <- rdrobust(y = panel_data$income, x = panel_data$nearest_store_distances,
                        c = cutoff, bwselect = "mserd", kernel = "triangular")

### 2024-07-09 manuscript/main.tex
modified:   analysis/RD design analysis.Rmd 	deleted:    analysis/RD-design-analysis.tex 	deleted:    analysis/donut_robust.tex 	modified:   figures/RD_Plot_1st_Order.pdf 	new file:   figures/RD_Plot_1st_Order_robust.pdf 	modified:   figures/RD_Plot_2nd_Order.pdf 	new file:   figures/RD_Plot_2nd_Order_robust.pdf 	modified:   figures/RD_Plot_3rd_Order.pdf 	new file:   figures/RD_Plot_3rd_Order_robust.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscr

@@

To determine the optimal radius of influence, this research employs a RDD on the neighborhood level transaction data to examine the influential radius of offline real estate brokerages. The dependent variable in this analysis is the transaction revenue generated by Lianjia within a given community, while the independent variable is the community's proximity to the nearest Lianjia store. Given that stores are predominantly located within commercial districts, which typically encompass several streets no more than two kilometers in diameter, it is assumed that a requisite number of stores within each district is essential to sustain revenue generation in that community. In addition, Lianjia adopts a pedestrian shed strategy, also known as a 5-minute walking distance (approximately 400 meters) strategy, which means that customers should be accessible within a 5-minute walk to the nearest Lianjia store to reduce the visiting cost. Building on this premise, the study further investigates the existence of an optimal influence radius within shopping districts, defined as the distance radius within which the presence of a Lianjia optimally increases transaction revenues. At the same time, the study also examines the hypothesis that beyond this optimal radius, the impact on transaction revenues diminishes as a result of the strategic store layout decisions implemented by Lianjia.

@@

From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the lianjia's 5-minute walk distance policy (400 meters). The observed decline in the Lianjia's influence is marked and suggests a pronounced reduction in its impact on the system overall within our study sample. This phenomenon can be attributed to the implementation of the Lianjia's proximity to customers policy, which is evidenced at the data level. Table \ref{tab:rd_bandwidth_kernel_results} considers different kernel and bandwidth choices, and the results are consistent with the 410 meters radius. The only non-significance is the CER-optimal bandwidth selector with triangular kernel, which is because the selected bandwidth is too small to capture the discontinuity. The results are robust to different bandwidth and kernel choices, which suggests that the 410 meters is the optimal radius for Lianjia's offline stores.

@@

\bibitem[Christensen and Timmins(2022)]{RePEc:ucp:jpolec:doi:10.1086/720140}
Christensen, P., and C. Timmins. 2022. Sorting or Steering: The Effects of Housing Discrimination on Neighborhood Choice. \textit{Journal of Political Economy}, 130(8), 2110-2163.
  \end{thebibliography}
\end{singlespace}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Table \ref{}
\input{../result_tables/donut_robust.tex}

>>>>

% THIS SHOULD BE REVISED!!!

@@

To determine the optimal radius of influence, this research employs a RDD on the neighborhood level transaction data to examine the influential radius of offline real estate brokerages. The dependent variable in this analysis is the transaction revenue generated by Lianjia within a given community, while the independent variable is the community's proximity to the nearest Lianjia store. Given that stores are predominantly located within commercial districts, which typically encompass several streets no more than two kilometers in diameter, it is assumed that a requisite number of stores within each district is essential to sustain revenue generation in that community. In addition, Lianjia adopts a pedestrian shed strategy, also known as a 5-minute walking distance (approximately 400 meters) strategy, which means that customers should be accessible within a 5-minute walk to the nearest Lianjia store to reduce the visiting cost. Moreover, this is consistent with the govvernment's proposal policy that most of the living facilities should be within five-minute pedestrian scale distance \citep{GB50180-2018}. Besides, some other paper also demonstrated that in other fields, the distance above 5-minute walk distance can create significant drop in most of hte properties \citep{liu2023chrono-urbanism}.

Building on this premise, the study further investigates the existence of an optimal influence radius within shopping districts, defined as the distance radius within which the presence of a Lianjia optimally increases transaction revenues. At the same time, the study also examines the hypothesis that beyond this optimal radius, the impact on transaction revenues diminishes as a result of the strategic store layout decisions implemented by Lianjia.

@@

%% Need to revise

From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the lianjia's 5-minute walk distance policy (approximately 410 meters). The observed decline in the Lianjia's influence is marked and suggests a pronounced reduction in its impact on the system overall within our study sample. This phenomenon can be attributed to the implementation of the Lianjia's proximity to customers policy, which is evidenced at the data level. Table \ref{tab:rd_bandwidth_kernel_results} considers different kernel and bandwidth choices, and the results are consistent with the 410 meters radius. The only non-significance is the CER-optimal bandwidth selector with triangular kernel, which is because the selected bandwidth is too small to capture the discontinuity. The results are robust to different bandwidth and kernel choices, which suggests that the 410 meters is the optimal radius for Lianjia's offline stores.

\footnote{Note that we should not use bandswidths that within too small of the distances above the Lianjia to the neighborhoods, and this is because our evaluation of the neighborhood is based on the centroid point of the neighborhood, and the store's distance to the centroid point is not necessarily means that it is not close to the neighborhood. Therefore, with distance very close to the neighborhood, we can also think they are approximately close.}

@@

\bibitem[Christensen and Timmins(2022)]{RePEc:ucp:jpolec:doi:10.1086/720140}
Christensen, P., and C. Timmins. 2022. Sorting or Steering: The Effects of Housing Discrimination on Neighborhood Choice. \textit{Journal of Political Economy}, 130(8), 2110-2163.

\bibitem[MOHURD(2018)]{GB50180-2018}
  Ministry of Housing and Urban-Rural Development of China. 2018. \textit{Urban Residential Area Planning and Design Standard (GB50180-2018)}. Available from \url{http://www.moe.gov.cn/jyb_xwfb/xw_zt/moe_357/jyzt_2019n/2019_zt13/zcwj/201906/t20190606_384732.html}. (in Chinese).

  \bibitem[Liu et al.(2023)]{liu2023chrono-urbanism}
  Liu, D., M.-P. Kwan, L. Wang, Z. Kan, J. Wang, and J. Huang. 2023. Development of a Chrono-Urbanism Status Composite Index under the 5/10/15-Minute City Concept Using Social Media Big Data. \textit{Tijdschrift voor Economische en Sociale Geografie}, Early View. doi:10.1111/tesg.12613.
  \end{thebibliography}
\end{singlespace}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

One common concern in RDD is the potential for manipulation around the cutoff, which could invalidate the results. To address this, a "donut hole" robustness check can be implemented, where observations close to the cutoff are excluded to ensure that the results are not driven by manipulation or other local irregularities. In this study, we apply a donut hole robustness check to an RDD with a cutoff of 410 meters. Specifically, we sequentially exclude observations within certain distances from the cutoff and re-estimate the treatment effect. The distances considered for exclusion are 100, 125, 150, 175, 200, 225, and 250 meters. This method helps to verify the robustness of the estimated treatment effects to the exclusion of data points near the cutoff.

Table \ref{tab:rd_robust_results} shows the donut hole effect, we exclude the samples within

\begin{figure}[ht]
  \centering
  \subfloat[RDD plot with first order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_1st_Order_robust.pdf}\label{fig:RD_Plot_1st_Order_Robust}}
  \hfill % Adds horizontal space between figures
  \subfloat[RDD plot with second order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_2nd_Order_robust.pdf}\label{fig:RD_Plot_2nd_Order_Robust}}
  \hfill % Adds horizontal space between figures
  \subfloat[RDD plot with third order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_3rd_Order_robust.pdf}\label{fig:RD_Plot_3rd_Order_Robust}}
  \caption{RDD design Robustness Check using log(income)}
  \label{fig:RD_design_Robust}
\end{figure}

\input{../result_tables/rdd_result_summary_robust.tex}

% Imbens, G. W., & Lemieux, T. (2008). Regression Discontinuity Designs: A Guide to Practice. Journal of Econometrics, 142(2), 615-635.
% Lee, D. S., & Lemieux, T. (2010). Regression Discontinuity Designs in Economics. Journal of Economic Literature, 48(2), 281-355.
\input{../result_tables/donut_robust.tex}
